Incentivizing Exploration with Unbiased History

### 2018-10-17 llevel.tex
update thm 6.5

\begin{proof}
We are going to show that for each $l$ and $a$ there exists $u_a$ such that agents in groups $G_{l,1,u_a},...,G_{l,S,u_a}$ and $\Gamma_{l,1,u_a},...,\Gamma_{l,S,u_a}$ all pull arm $a$. This suffices to prove the claim.

@@

Recall in the proof of Theorem \ref{thm:llevel}, $\varepsilon_l =\Theta(1/\sqrt{T_l S})$ for $l \in [L-1]$ and $\varepsilon_0 = 1$. Consider two cases:
\begin{itemize}
\item $\Delta < \varepsilon_{L-1} S$. In this case, notice that even always picking the sub-optimal arm gives expected regret at most $T(\mu_1-\mu_2) = T\Delta = O(T^{1/2} polylog(T))$. On the other hand, $T^{1/2} = O(polylog(T)/\Delta)$. Therefore, the expected regret is $O(\min(1/\Delta, T^{1/2})polylog(T))$.
\item $\Delta \geq \varepsilon_{L-1} S$. In this case, we can find $l \in \{2,...,L\}$ such that $\varepsilon_{l-1} S\leq \Delta < \varepsilon_{l-2} S$. By Claim \ref{clm:l2_exploit}, we can upper bound the expected regret by
\begin{align*}
&\Delta \cdot (T_1 \GdT S^2  +T_2 S^3+ \cdots T_{l-1} S^3)\\
=& O(\Delta T_{l-1}S^3) \\
=&O(\Delta T_{l-2}S^7) \\
=&O(\Delta\cdot  \frac{1}{\varepsilon^2_{l-2}}\cdot S^6)\\
=&O(\Delta \cdot \frac{1}{\Delta^2}\cdot S^8)\\
=&O(polylog(T)/\Delta).
\end{align*}
We also have $1/\Delta \leq 1/(\varepsilon_{L-1}S)= O(T^{1/2})$. Therefore, the expected regret is \\$O(\min(1/\Delta, T^{1/2})polylog(T))$.
\end{itemize}
\end{proof}

@@

\begin{theorem}
Let the number of arms $K$ to be a constant larger than 2. Let $\Delta$ to be the difference between means of best and second best arms. We have an $L$-level recommendation policy with expected regret $O(\min(1/\Delta, T^{1/2})polylog(T))$. This $L$-level recommendation policy does not need to know $\Delta$. Moreover, agent $t$ observes a subhistory of size at least $\Omega( \lfloor t/polylog(T)\rfloor)$. 
\end{theorem}

\xhdr{Proof Sketch.}
We first extend the clean events (i.e. $W_1,W_2,W_3,W_4$) in Theorem \ref{thm:llevel} to the case when $K$ is larger than 2. $W_1$ and $W_2$ extend naturally: we still set $W_1 = \bigcap_{a,s}W_1^{a,s}$ and $W_2 = \bigcap_{t,a,t_1,t_2} W_2^{t,a,t_1,t_2}$. The difference is that now $a$ is taken over $K$ arms instead of 2 arms. For $W_3$, we change the definition $W_3^{l,a} = \bigcup_u \left(W_3^{l,u,a,high}  \cap \left(\bigcap_{a' \neq a} W_3^{l,u,a',low}\right) \right)$ and $W_3 = \bigcap_{l,a} W_3^{l,a}$. We extend $W_4$ in a similar way: define $W^{a}_4$ as $\bigcup_u \left(W_4^{u,a,high} \cap \left(\bigcap_{a' \neq a} W_4^{u,a',low}\right) \right)$ and $W_4 = \bigcap_a W^a_4$. Since $K$ is a constant, it's easy to check that the same proof technique shows that the intersection of these clean events happen with probability  $1-O(1/T)$.

\qed

>>>>

\begin{proof}
We are going to show that for each $l$ and arm $a$ there exists $u_a$ such that agents in groups $G_{l,1,u_a},...,G_{l,S,u_a}$ and $\Gamma_{l,1,u_a},...,\Gamma_{l,S,u_a}$ all pull arm $a$. This suffices to prove the claim.

@@

Recall in the proof of Theorem \ref{thm:llevel}, $\varepsilon_l =\Theta(1/\sqrt{T_l S})$ for $l \in [L-1]$ and $\varepsilon_0 = 1$. Consider two cases:
\begin{itemize}
\item $\Delta < \varepsilon_{L-1} S$. In this case, notice that even always picking the sub-optimal arm gives expected regret at most $T(\mu_1-\mu_2) = T\Delta = O(T^{1/2} polylog(T))$. On the other hand, $T^{1/2} = O(polylog(T)/\Delta)$. Therefore, the expected regret is $O(\min(1/\Delta, T^{1/2})polylog(T))$.
\item $\Delta \geq \varepsilon_{L-1} S$. In this case, we can find $l \in \{2,...,L\}$ such that $\varepsilon_{l-1} S\leq \Delta < \varepsilon_{l-2} S$. By Claim \ref{clm:l2_exploit}, we can upper bound the expected regret by
\begin{align*}
&\Delta \cdot (T_1 \GdT S^2  +T_2 S^3+ \cdots T_{l-1} S^3)\\
=& O(\Delta T_{l-1}S^3) \\
=&O(\Delta T_{l-2}S^7) \\
=&O(\Delta\cdot  \frac{1}{\varepsilon^2_{l-2}}\cdot S^6)\\
=&O(\Delta \cdot \frac{1}{\Delta^2}\cdot S^8)\\
=&O(polylog(T)/\Delta).
\end{align*}
We also have $1/\Delta \leq 1/(\varepsilon_{L-1}S)= O(T^{1/2})$. Therefore, the expected regret is \\$O(\min(1/\Delta, T^{1/2})polylog(T))$.
\end{itemize}

Finally we discuss about the subhistory sizes. We know that agents in level $l$ observes the history of all agents below level $l-2$ (including level $l-2$). It is easy to check that the ratio between the number of agents below level $l$ and the number of agents below level $l-2$ is bounded by $O(polylog(T))$. Therefore our statement about the subhistory sizes holds.
\end{proof}

@@

\begin{theorem}
Theorem \ref{thm:llevel} and Corollary \ref{cor:llevel} can be extended to the case when $K$ is constant larger than 2. In the extension of Corollary \ref{cor:llevel}, $\Delta$ is defined as the difference between means of the best and the second best arm.
\end{theorem}

\xhdr{Proof Sketch.}
We still wlog assume arm 1 has the highest mean (i.e. $\mu_1 \geq \mu_a, \forall a \in \A$. We first extend the clean events (i.e. $W_1,W_2,W_3,W_4$) in Theorem \ref{thm:llevel} to the case when $K$ is larger than 2. $W_1$ and $W_2$ extend naturally: we still set $W_1 = \bigcap_{a,s}W_1^{a,s}$ and $W_2 = \bigcap_{t,a,t_1,t_2} W_2^{t,a,t_1,t_2}$. The difference is that now $a$ is taken over $K$ arms instead of 2 arms. For $W_3$, we change the definition $W_3^{l,a} = \bigcup_u \left(W_3^{l,u,a,high}  \cap \left(\bigcap_{a' \neq a} W_3^{l,u,a',low}\right) \right)$ and $W_3 = \bigcap_{l,a} W_3^{l,a}$. We extend $W_4$ in a similar way: define $W^{a}_4$ as $\bigcup_u \left(W_4^{u,a,high} \cap \left(\bigcap_{a' \neq a} W_4^{u,a',low}\right) \right)$ and $W_4 = \bigcap_a W^a_4$. Since $K$ is a constant, it's easy to check that the same proof technique shows that the intersection of these clean events happen with probability  $1-O(1/T)$. So the case when some clean event does not happen contributes $O(1)$ to the expected regret.

Now we proceed to extend Claim \ref{clm:l2_explore} and Claim \ref{clm:l2_exploit}. The statement of Claim \ref{clm:l2_explore} should be changed to ``For any arm $a$ and $2\leq l \leq L$, if $\mu_1 - \mu_a \leq \varepsilon_{l-1}$, then for any $u \in [S]$, there are at least $T_l$ pulls of arm $a$ in groups $G_{l,u,1},G_{l,u,2}, ... ,G_{l,u,S}$ and there are at least $T_lS(S-1)$ pulls of arm $a$ in the $l$-th level $\Gamma$-groups''. The statement of Claim \ref{clm:l2_exploit} should be changed to ``For any $2 \leq l \leq L$, if $\varepsilon_{l-1} S\leq \mu_1 - \mu_a < \varepsilon_{l-2} S$, there are no pulls of arm $a$ in groups with level $l,...,L$.''

The proof of Claim \ref{clm:l2_exploit} can be easily changed to prove the new version by changing ``arm 2'' to ``arm $a$''. The proof of Claim \ref{clm:l2_explore} needs some additional argument. In the proof of Claim \ref{clm:l2_explore}, we show that $\hat{\mu}_a^t - \hat{\mu}_{3-a} > 0 $ for agent $t$ in the chosen groups. When extending to more than 2 arms, we need to show $\hat{\mu}_a^t - \hat{\mu}_{a'}^t > 0$ for all arm $a' \neq a$. The proof of Claim \ref{clm:l2_explore} goes through if $\mu_1- \mu_{a'} \leq \varepsilon_{l-2}$ since then there will be enough arm $a'$ pulls in level $l-1$. We need some additional argument for the case when $\mu_1 - \mu_{a'} > \varepsilon_{l-2}$. Since $\mu_1- \mu_{a'} > \varepsilon_{l-2} > \varepsilon_{l-1}S$, we can use the same proof of Claim \ref{clm:l2_exploit} (which rely on Claim \ref{clm:l2_explore} but for smaller $l$'s) to show that there are no arm $a'$ pulls in level $l$ and therefore $\hat{\mu}_a^t - \hat{\mu}_{a'}^t > 0$.

Finally we proceed to bound the expected regret conditioned on the intersection of clean events happens. The proofs of Theorem \ref{thm:llevel} and Corollary \ref{cor:llevel} bound it by consider the regret from pulling the suboptimal arm (i.e. arm 2). When extending to more than 2 arms, we can do the exactly same argument for all arms except arm 1. This will blow up the expected regret by a factor of $(K-1)$ which is a constant.
\qed
